### 2025-05-06 MSc.tex
Forgot to push?

\documentclass[a4paper,12pt,twoside,BCOR=10mm]{scrbook}

@@

% Packages
% BETRI TÖFLUR OG LISTAR
\usepackage{booktabs}         % Fyrir betri töflur
\usepackage{caption}          % M.a. aukabil á undan töflufyrirsögnum
\captionsetup{font=small,   % Smærra letur á mynda- og töflutexta,
              labelfont=bf, % "Mynd 1" og "Tafla 2" feitletrað 
              margin=2cm,
              skip = 0.5\baselineskip} 
\usepackage[utf8]{inputenc}
\usepackage[icelandic, english]{babel}
\usepackage{t1enc}
\usepackage{graphicx}
\usepackage[intoc]{nomencl}
\usepackage{enumerate,color}
\usepackage{url}
\usepackage[pdfborder={0 0 0}]{hyperref}
\BeforeTOCHead[toc]{\cleardoublepage\pdfbookmark{\contentsname}{toc}} % Add Table of Contents to PDF "bookmark" table of contents
\usepackage{appendix}
\usepackage{eso-pic}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{subcaption}
%\usepackage[sf,normalsize]{subfigure}
\usepackage[format=plain,labelformat=simple,labelsep=colon]{caption}
\usepackage{placeins}
%\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{xspace}
\usepackage{float}
\usepackage{caption}
% Packages used for title page layout
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{arydshln}
\usepackage{acronym}
\usetikzlibrary{positioning}
\pgfkeys{/pgf/number format/.cd,fixed,precision=2}

@@

\printbibliography
\appendix
\include{Appendicies/AppendixA}

>>>>

\documentclass[a4paper,12pt,twoside,BCOR=10mm,openany]{scrbook}

@@

% Packages
% BETRI TÖFLUR OG LISTAR
\usepackage{booktabs}         % Fyrir betri töflur
\usepackage{caption}          % M.a. aukabil á undan töflufyrirsögnum
\captionsetup{font=small,   % Smærra letur á mynda- og töflutexta,
              labelfont=bf, % "Mynd 1" og "Tafla 2" feitletrað 
              margin=2cm,
              skip = 0.5\baselineskip} 
\usepackage[utf8]{inputenc}
\usepackage[icelandic, english]{babel}
\usepackage{t1enc}
\usepackage{graphicx}
\usepackage[intoc]{nomencl}
\usepackage{enumerate,color}
\usepackage{url}
\usepackage[pdfborder={0 0 0}]{hyperref}
\BeforeTOCHead[toc]{\cleardoublepage\pdfbookmark{\contentsname}{toc}} % Add Table of Contents to PDF "bookmark" table of contents
\usepackage{appendix}
\usepackage{eso-pic}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{subcaption}
%\usepackage[sf,normalsize]{subfigure}
\usepackage[format=plain,labelformat=simple,labelsep=colon]{caption}
\usepackage{placeins}
%\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{xspace}
\usepackage{float}
\usepackage{caption}
% Packages used for title page layout
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{arydshln}
\usepackage{acronym}
% Packages used for header vertical space along with the methods that set the spacing
% Adjust spacing before and after chapters
\RedeclareSectionCommand[
  beforeskip=-0pt, % Space before the chapter title
  afterskip=0pt    % Space after the chapter title
]{chapter}

% Adjust spacing before and after sections
\RedeclareSectionCommand[
  beforeskip=0pt,   % Space before the section title
  afterskip=1pt     % Space after the section title
]{section}

% Adjust spacing before and after subsections
\RedeclareSectionCommand[
  beforeskip=0pt,   % Space before the subsection title
  afterskip=1pt     % Space after the subsection title
]{subsection}

\usetikzlibrary{positioning}
\pgfkeys{/pgf/number format/.cd,fixed,precision=2}

@@

\printbibliography
\appendix
\include{Appendicies/AppendixA}
\include{Appendicies/AppendixB}
